### 2021-03-12 results/draft.tex
revised the last sentence in the third paragraph in Introduction

\ \ \ \ \ \ \ \ \ \ 
Integrated species distribution models (IDMs) are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al. 2020; Miller et al. 2019).

The models combine the different type of data with strengths and weaknesses in a single model ().
For example, scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when we use single data (Pacifici et al. 2017; Miller et al. 2019).

\ \ \ \ \ \ \ \ \ \ 
Tokyo Bay is a large enclosed coastal sea in Japan. There are many commercially important species for fisheries that are called "Edomae" in Tokyo Bay because these species have been used for Sushi since Edo Era (about 400 years ago). Catch weight of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution). Catch statistics (total catch weight in each species, efforts, and geographic location of fishing) have been collected for stock assessment since \textcolor{red}{1990} by prefectures around Tokyo Bay. The strengths of this data are the direct evidence that a focal species occupies a location of fishing and abundant because of widely collected in Tokyo Bay.  On the other hand, weakness of this data is like a opportunistic data because the data is likely to be biased towards areas to high density of focal species due to commercially fishes, consequently less zero data. In addition to this catch statistics, scientific survey of eDNA has been conducted monthly since 2018 for biodiversity monitoring because biodiversity also may decreased due to human-induced environmental changes in Tokyo Bay (Hongo et al., submitted). The strengths are that the data is systematically collected data and includes zero data, while the weaknesses are that the data is less abundant due to spatial restriction of the survey and includes spatial uncertainty in the occurrence of eDNA as description in above.

\ \ \ \ \ \ \ \ \ \ 
In this paper, 
%to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM). 
to infer spatial distribution of species from eDNA, we first make a spatial distribution model wichi considers spatial uncertainty of eDNA by using an integrated spatial distribution model. 
We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 
%The predicted spatial distribution of four fish form our model reduced

>>>>

\ \ \ \ \ \ \ \ \ \ 
Integrated species distribution models (IDMs) are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
% As alternative approach to over come the spatial uncertainty of eDNA, statistical modeling approach should be a useful approach.
%The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al. 2020; Miller et al. 2019).
%The model use the different type of data with strengths and weaknesses, such as scientific survey data (high quality but not abundant) and opportunistic citizen data (low quality but abundant) , and combine in a single model (Isaac et al. 2020; Miller et al. 2019).
The models combine the different type of data with strengths and weaknesses in a single model. For example, the model can use both scientific survey data, which is high quality but less abundant due to restriction of cost, and citizen data, which is widely collected and abundant but may be low quality due to not using consistent field methods in a model.
%scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the inference of the spatial distribution form the model should be reduced about spatial uncertainty of eDNA and should be improved.   
%したがって，統合モデルにより『生物がその場所に生息する』という情報をeDNAに加えることで，eDNA
%したがって，eDNAデータと新たなデータ（『生物がその場所に生息する』という情報を持つ）を使って統合モデルを構築すれば，eDNAデータに対する空間的な不確実性は減少し，eDNAから推定される空間分布の精度は上昇することが期待される．

%\ \ \ \ \ \ \ \ \ \ 
%Tokyo Bay is a large enclosed coastal sea in Japan. There are many commercially important species for fisheries that are called "Edomae" in Tokyo Bay because these species have been used for Sushi since Edo Era (about 400 years ago). Catch weight of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution). Catch statistics (total catch weight in each species, efforts, and geographic location of fishing) have been collected for stock assessment since \textcolor{red}{1990} by prefectures around Tokyo Bay. The strengths of this data are the direct evidence that a focal species occupies a location of fishing and abundant because of widely collected in Tokyo Bay.  On the other hand, weakness of this data is like a opportunistic data because the data is likely to be biased towards areas to high density of focal species due to commercially fishes, consequently less zero data. In addition to this catch statistics, scientific survey of eDNA has been conducted monthly since 2018 for biodiversity monitoring because biodiversity also may decreased due to human-induced environmental changes in Tokyo Bay (Hongo et al., submitted). The strengths are that the data is systematically collected data and includes zero data, while the weaknesses are that the data is less abundant due to spatial restriction of the survey and includes spatial uncertainty in the occurrence of eDNA as description in above.

\ \ \ \ \ \ \ \ \ \ 
If we use one or more data that include the information about species existence in addition to eDNA data and infer the spatial distribution with combing these data by using IDMs, the spatial uncertainty of eDNA should recuse and the accuracy of prediction should increase.

統合モデルを使えば，eDNAデータだけで空間分布を推定するよりも推定精度が上がり，
In this paper, 
%to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM). 
to infer spatial distribution of species from eDNA, we first make a spatial distribution model wichi considers spatial uncertainty of eDNA by using an integrated spatial distribution model. 
We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 
%The predicted spatial distribution of four fish form our model reduced
